---
title: "First Steps"
output: html_notebook
---


## Build staged trees 

```{r}
library(stagedtrees)
## we use data stored in contingency table 
## but it works also with data.frame objects.
data("Titanic") 
```

### Directly from data

We can use the functions `full` or `indep` to build 
saturated or fully independent staged trees. 

```{r}
model_f1 <- full(Titanic, order = c("Class", "Age", "Sex", "Survived"))
model_f1
```

By default `join_unobserved = TRUE` and thus unobserved situations are merged 
into a *special* stage (by default called `name_unobserved = "UNOBSERVED"`). 

For example for `model_f1`:

```{r}
stages(model_f1, var = "Sex") 

## we can check which path lead to the unobserved situation 
get_path(model_f1, var = "Sex", stage = "UNOBSERVED")
```


```{r}
model_f2 <- full(Titanic, order = c("Class", "Age", "Sex", "Survived"),
                 join_unobserved = FALSE)
model_f2
```

What is a staged tree `sevt` object ? 
```{r}
attributes(model_f1)
```
the `tree` element represent the order of the variable and their levels:
```{r}
model_f1$tree
```


### Build staged trees manually 

We can also use directly the `sevt` constructor 
and build staged tree structures manually:

```{r}
tree <- list(Class = c("1st", "2nd", "3rd", "Crew"),
             Age = c("Child", "Adult"),
             Sex = c("Male", "Female"),
             Survived = c("No", "Yes"))
model_f0 <- sevt(tree, full = TRUE)
model_f0

### alternatively we can also directly call sevt on the data
# model_f0 <- sevt(Titanic, order = c("Class", "Age", "Sex", "Survived"), 
#                  full = TRUE)
```

So what is the difference between `full` or `indep` and `sevt` ? 

```{r}
BIC(model_f1)

BIC(model_f0)
```

The functions `full` and `indep` will both construct the staged tree object, 
attach the data in ctables and compute probabilities.
While the `sevt` constructur will just build the staged tree structure 
but will not *fit* the model to data. 
Nevertheless, we can fit `model_f0` to the Titanic data with the
`sevt_fit` function: 
```{r}
model_f0_fitted <- sevt_fit(model_f0, data = Titanic, lambda = 0)
```

Alternatively we can even isolate the unobserved situations with 
`join_unobserved`,
```{r}
## this is equivalent to full(Titanic) but slower..
model_f0 |> sevt_fit(data = Titanic, lambda =0) |> join_unobserved()
```


