---
title: "Estimate staged tree structures"
output: html_notebook
---

```{r}
library("stagedtrees")
mod_f <- full(Titanic)
mod_i <- indep(Titanic)
```

All algorithms for learning the stages are implemented 
in the `stages_*` functions
and start from a given `sevt` object (usually built with `full` or `indep`). 


### Hill-climbing algorithms 

```{r}
mod1 <- stages_bhc(mod_f) ## backward hill-climbing
mod1a <- stages_fbhc(mod_f) ## fast backward
mod2 <- stages_hc(mod_i) ## hill climbing

BIC(mod1, mod2)
```

```{r, fig.show='hold'}
par(mfrow=c(1,2))
plot(mod1, main = "stages_bhc")
plot(mod2, main = "stages_hc")
```

#### Changing the score

```{r}
## use -AIC as score, the score is always maximised!!
mod1a <- stages_bhc(mod_f, score = function(x) -AIC(x))

## use logLik as score
mod2a <- stages_hc(mod_i, score = logLik) 
#mod1b <- stages_bhc(mod_f, score = logLik)

## why mod2a is not equal to mod_f ?
#plot(mod1b)
plot(mod2a)
```


### Clustering algorithms

```{r}
mod3 <- stages_hclust(mod_f, k = 2)
mod4 <- stages_kmeans(mod_f, k = c(Sex = 2, Age = 3, Survived = 4))
```



```{r, fig.show='hold'}
par(mfrow=c(1,2))
plot(mod3)
plot(mod4)
```

### Additional arguments

The `scope` argument limit the search to one of the variables.
```{r}
mod5 <- stages_bhc(mod_f, scope = "Survived")
plot(mod5)
```

The `ignore` argument is used to exclude some stages from the search. 
By default it is equal to the `$name_uonberved` field (usually `"UNOBSERVED"`)
```{r}
## we make a new starting model 
mod_start <- mod_f 
## we fix some stages
mod_start$stages$Age[1:4] <- "MYSTAGE"
mod_start$stages$Survived[c(1,5,10)] <- "FIX"
## we need to refit the model!!!
mod_start <- sevt_fit(mod_start)

## could we also ignore the UNOBSERVED? 
mod6 <- stages_bhc(mod_start, ignore = c("MYSTAGE", "FIX"))

## we plot with some special colors to higlight the unchanged stages
colors <- make_stages_col(mod6, col = function(stages){
    hcl.colors(n = length(stages))
})
colors$Age["MYSTAGE"] <- "purple"
colors$Survived["FIX"] <- "orange"
plot(mod6, col = colors)
```


### Order search


```{r}
mod7 <- search_greedy(Titanic)
plot(mod7)
```
```{r}
mod8 <- search_best(Titanic)
plot(mod8)
```

