---
title: "Comparing Models"
output: html_notebook
---


We can start from two simple models obtained with 
the `stages_bhc` and `stages_hc` functions. 

```{r}
library("stagedtrees")
model1 <- Titanic |> full() |> stages_bhc()
model2 <- Titanic |> indep() |> stages_hc()
```

We plot them side by side once more, 

```{r, fig.show='hold'}
par(mfrow = c(1,2))
plot(model1, main = "Model 1 (BHC-full)")
plot(model2, main = "Model 2 (HC-indep)")
```

We can see the stage structures for `Age` and `Survived` is 
different ... but how much? 
We can use the `compare_stages` function for that.

In its simpler usage, the `compare_stages` function just check 
if two staged trees have the same stage structure. 

```{r}
compare_stages(model1, model2)
```

Alternatively we can plot the differences in the tree, 
```{r}
## try also method = "stages", check ?compare_stages
## the "naive" method just compare the stages vectors afterr a standard renaming 
compare_stages(model1, model2, method = "hamming", plot = TRUE)
```

You can also use directly `hamming_stages`and `diff_stages`

```{r}
hamming_stages(model1, model2) 
```

```{r}
diff_stages(model1, model2)
```

Or you can check inclusion of stages with 

```{r}
inclusions_stages(model1, model2)
```


## Likelihood-ratio test

```{r}
try(lr_test(model1, model2))
```

```{r}
model1.1 <- join_stages(model1, "Sex", 3, 4)

lr_test(model1.1, model1)

model1.2 <- model1 
model1.2$stages$Sex <- c(1,2,3,4)
model1.2 <- sevt_fit(model1.2)

lr_test(model1, model1.2)
```





